Verifying Demonstrations

### 2018-05-31 paper/protocol.tex
Fixes intro in protocol, adds missing labels

We now present \PRIVO, a protocol for securely and PRIvately Verifying PROtest 
Outcomes.
The protocol consists of five phases: the setup, join, participation, 
submission and verification phases.
The setup is described in \cref{ProtocolSetup}.
The join, participation and submission phases are described in 
\cref{ProtocolDuring}.
Finally, the verification phase is described in \cref{ProtocolVerification}.

@@

\subsection{The setup phase}

@@

\subsection{Creating, joining, participating in a protest and submitting 
  proofs}

>>>>

We now present \PRIVO, a protocol for securely and privately verifying crowd 
counts.
The protocol consists of five phases: the setup, join, participation, 
submission and verification phases.
The setup is described in \cref{ProtocolSetup}.
The join, participation and submission phases are described in 
\cref{ProtocolDuring}.
Finally, the verification phase is described in \cref{ProtocolVerification}.

@@

\subsection{The setup phase}%
\label{ProtocolSetup}

@@

\subsection{Creating, joining, participating in a protest and submitting 
  proofs}%
\label{ProtocolDuring}
